abxD01 Paper

### 2015-04-08 Schubert_abxD01_mBio_2015.Rmd
Rename files to indicate mBio as journal
Update for new correlation file name

error_nochim <- error[error$numparents==1,]

error_rate <- 100 * sum(error$weight * error$error)/sum(error$weight)
```

@@

```{r top_dose_cfu_analysis}
cfu <- read.table(file="data/process/abxD1.counts")
cfu_top_dose <- cfu[cfu$experiment == "top_dose" & cfu$abx != "control",]
cfu_top_dose_summary <-aggregate(cfu_top_dose$CFU, by=list(cfu_top_dose$abx), summary)
treatments <- cfu_top_dose_summary$Group.1
cfu_top_dose_summary <- format(cfu_top_dose_summary$x, scientific=T, digits=2)
rownames(cfu_top_dose_summary) <- treatments
```

@@

```{r top_dose_correlation}
corr_data <- read.table(file="data/process/top_dose_corr.tsv", header=T)
families <- gsub(".*;", "", corr_data$taxonomy)
ave_corr_family_agg <- aggregate(corr_data$sig_corrs, by=list(families), function(x){ c(mean(x), length(x))})
ave_corr_family <- round(ave_corr_family_agg$x[,1], 2)
names(ave_corr_family) <- ave_corr_family_agg$Group.1

>>>>

error_nochim <- error_table[error_table$numparents==1,]

error_rate <- 100 * sum(error_nochim$weight * error_nochim$error)/sum(error_nochim$weight)
```

@@

@@

```{r top_dose_correlation}
corr_data <- read.table(file="data/process/correlation_analysis.tsv", header=T)
families <- gsub(".*;", "", corr_data$taxonomy)
ave_corr_family_agg <- aggregate(corr_data$sig_corrs, by=list(families), function(x){ c(mean(x), length(x))})
ave_corr_family <- round(ave_corr_family_agg$x[,1], 2)
names(ave_corr_family) <- ave_corr_family_agg$Group.1
